---
title: "Homework11"
author: "Laura Ludwig"
date: "November 18, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Brief Financial Data
### a. Extract the DAX time series
```{r data1}
DAX <- EuStockMarkets[,"DAX"] #Extract the DAX variable from the multivariate time series
```

Pull the DAX variable out of the multivariate time series.

### b. Plot the data
```{r plot1}
plot(DAX,col="blue",ann=FALSE)
title(main="DAX Stock Index Trend",xlab="Year",ylab="DAX Index Value")
abline(v=1997, col="red")
```

This plot shows the trend of the DAX Index value. There is an event of note in 1997, which is indicated by the red line.

### c. Decompose the Time Series
```{r decompose}
fit <- decompose(DAX,type="multiplicative")
plot(fit,col="blue")
abline(v=1997,col="red")
```

Decomposing the time series to show trend, seasonality and noise.

## Temperature Data
### a. Examining Data
```{r data2}
library(fpp2)
autoplot(maxtemp)
```

Maximum temperatures in Melbourne, Australia, given in Celsius, from 1971 to 2016.

### b. Subsetting to view 1990 and beyond
```{r subet2}
recent <- window(maxtemp,start=c(1990,1))
```

Subsetting the data from maxtemp to show 1990 and beyond.

### c. Forecasting 
```{r forecast2c}
forecast <- ses(recent, h=5)
plot(forecast)
lines(forecast$fitted,col="blue")
aicc<-forecast$model$aicc
```

Using Simple Exponential Smoothing, a five-year prediction is shown. The predicted values for each year in the dataset from 1990 forward are shown in blue.

### d. Damped Holt's Linear Trend
```{r forecast2d}
holtforecast <-holt(recent,h=5,damped=TRUE,inital="optimal")
plot(holtforecast)
lines(holtforecast$fitted,col="blue")
aiccHolt <- holtforecast$model$aicc
```

Using Holt linear trend (with damping), a five-year prediction is shown. The predicted values for each year in the dataset from 1990 forward are shown in blue.

### e. Comparing AICCs
```{r AICCs}
aicc
aiccHolt
```

The preferred model it typically the one with the smaller AICc value, in this case, the SES model. 

## The Wands Choose the Wizard
